### 2017-07-19 sheets/talk-11/sheet-11.tex

  Then verify that this construction imposes a functor $\int_\cat{C} \from
  \mathit{Psh}(\cat{C}) \to \CAT$.
\end{exercise}
\begin{answer}
  Indeed, the operation of $\sigma$ on such objects is a precomposition
  satisfying the naturality axiom:
  \[
    \int_\cat{C}\sigma(I, \rho) := (I, \sigma_I \rho)
  \]

  Let's check that $\int_\cat{C}$ indeed takes us into a category.
  \begin{itemize}
    \item objects are pairs $(I, \rho)$ where $I \in \cat{C}$ and $\rho \in \Gamma(I)$
    \item a morphism $(J, \rho') \to (I, \rho)$ is a morphism $f \from J \to I$
      in $\cat{C}$ such that $\rho' = \rho f$.
  \end{itemize}
  We need to check that we have composition and identities.

  With our definition of objects, we can consider first and second projections
  of the pairs separately. We can observe, that elements of first projection
  are elements in $\cat{C}$ which have required identities and composition
  under morphisms in $\cat{C}$ (which are also our morphisms). Then what
  remains is the second projection. Identities and composition are exactly our
  conditions on presheaves which also hold.

  Now we know the operation of $\int_\cat{C}$ on objects and arrows in
  $Psh(\cat{C})$.
\end{answer}

>>>>

  Then verify that this construction imposes a functor $\int_\cat{C} \from
  \mathit{Psh}(\cat{C}) \to \CAT$.
\end{exercise}
\begin{answer}
  Indeed, the operation of $\sigma$ on such objects is a precomposition
  satisfying the naturality axiom:
  \[
    \int_\cat{C}\sigma(I, \rho) := (I, \sigma_I \rho)
  \]
  where $\rho \in \Gamma(I), I \in \cat{C}$

  Let's check that $\int_\cat{C}$ takes us into a category. Recall the
  definition of $\int_\cat{C}\Gamma$:
  \begin{itemize}
    \item objects are pairs $(I, \rho)$ where $I \in \cat{C}$ and $\rho \in \Gamma(I)$
    \item a morphism $(J, \rho') \to (I, \rho)$ is a morphism $f \from J \to I$
      in $\cat{C}$ such that $\rho' = \rho f$.
  \end{itemize}

  We know our objects and morphisms, we get identities and composition by
  the equations $\rho 1 = \rho$, $(\rho f) g = \rho (f g)$ and the fact that
  morphisms $f$ are valid morphisms in the category $\cat{C}$.

  Let's now see that $\int_\cat{C}\sigma$ is a functor in $\CAT$. We have a
  mapping for objects $\int_\cat{C}\sigma(I, \rho)$ given above. The operation
  on arrows is as follows, where $f \from J \to I$, $g \from K \to J$:
  \[
    \int_\cat{C}\sigma(f) := \sigma_{I \to J} \Gamma_f
  \]
  Then, keeping in mind that composition $fg$ is applied on the right we get
  $\int_\cat{C}\sigma(fg) = \sigma_{I \to K} \Gamma_{fg} = \sigma_{I \to K}
  \lambda \rho.\rho (fg) = \sigma_{I \to K} \lambda \rho. (\rho f)g = \sigma_{J
  \to K} (\sigma_{I \to J} \lambda \rho.\rho f) g = (\sigma_{J \to K} \lambda
  \rho.\rho g) (\sigma_{I \to J} \lambda.\rho f) = (\sigma_{J \to K} \Gamma_g)
  (\sigma_{I \to J} \Gamma_f)$. Which, together with $\rho 1 = \rho$ confirms
  that $\int_\cat{C}\sigma$ is indeed a functor.

  Thus, we conclude that $\int_\cat{C} \from \mathit{Psh}(\cat{C}) \to \CAT$ is
  a functor.
\end{answer}
